---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mixRSVP

The goal of mixRSVP is to mixture model temporal errors in reports of an item from an array or a stream, presently using a mixture model of uniform and Gaussian distributions.
[Here](https://alexholcombe.wordpress.com/2015/04/05/reporting-items-from-a-stream-and-mixture-modeling-to-reveal-buffering-and-a-bottleneck/) is an explanation of what the hell that means.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## History

Patrick Goodbourn programmed mixture modeling RSVP serial position errors in MATLAB. [Certifiedwaif](https://github.com/certifiedwaif/) did initial [port](https://github.com/certifiedwaif/AttentionalBlink) it to R, and then Alex [functionfied and improved things](https://github.com/alexholcombe/MixtureModelRSVP) before making it into this package.
