---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mixRSVP

mixRSVP mixture models temporal errors in reports of an item from an array or a stream, presently using a mixture model of uniform and Gaussian distributions.
[Here](https://alexholcombe.wordpress.com/2015/04/05/reporting-items-from-a-stream-and-mixture-modeling-to-reveal-buffering-and-a-bottleneck/) is an explanation of what that means.

## Installation

```{r install, eval=FALSE}
install_packages('devtools')  #if you don't have devtools already
library('devtools') 
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE) #No longer works
#Because of a change in devtools, you have to do this long command below to get the vignettes built
devtools::install_github('alexholcombe/mixRSVP', build = TRUE, build_opts = c("--no-resave-data", "--no-manual"))
```

## Example

Fit some of one of the provided datasets and plot the histogram of serial position errors together with the fitted curve.


```{r example, eval=FALSE}
 df <-  subset(P2E2pilot, subject=="CB" & target==1 & condition==1)
 plot_hist_with_fit(df, -11, 11, df$targetSP, 16, TRUE, TRUE, TRUE)
```

## Help

Type `?mixRSVP` or `?<FUNCTIONNAME>` and look at the vignettes that show examples of what you can do.

```{r vignettes, eval=FALSE}
vignette(package='mixRSVP')
```
## To-do

Still get warnings indicating pnorm is called with negative sigma,
"Got NaN as a result of calling pnorm with: 0.5 3.66418579969812 -9.1e-05"
Don't know why because sigma given bounds that greater than zero. Maybe function fitter still goes outside the bounds slight, and tightening the bounds will fix this?

Also get:
"Error in eigen(nhatend) : infinite or missing values in 'x'"

## History

Patrick Goodbourn programmed mixture modeling of RSVP serial position errors in MATLAB. [Certifiedwaif](https://github.com/certifiedwaif/) did initial [port](https://github.com/certifiedwaif/AttentionalBlink) of this to R, largely using automated code translation, and then Alex [functionfied and improved things](https://github.com/alexholcombe/MixtureModelRSVP) before making it into [this package](https://github.com/alexholcombe/mixRSVP).
