---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mixRSVP

The goal of mixRSVP is to mixture model temporal errors in reports of an item from an array or a stream, presently using a mixture model of uniform and Gaussian distributions.
[Here](https://alexholcombe.wordpress.com/2015/04/05/reporting-items-from-a-stream-and-mixture-modeling-to-reveal-buffering-and-a-bottleneck/) is an explanation of what the hell that means.

## Installation

```{r install}
library('devtools') #first install_packages('devtools') if you don't have it already
devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)
```

## Example

Fit some of one of the provided datasets and plot the histogram of serial position errors together with the fitted curve.


```{r example}
 df <-  subset(P2E2pilot,subject=="CB" & target==1 & condition==1)
 plot_hist_with_fit(df, -11, 11, df$targetSP, 16, TRUE, TRUE, TRUE)
```

## History

Patrick Goodbourn programmed mixture modeling RSVP serial position errors in MATLAB. [Certifiedwaif](https://github.com/certifiedwaif/) did initial [port](https://github.com/certifiedwaif/AttentionalBlink) it to R, and then Alex [functionfied and improved things](https://github.com/alexholcombe/MixtureModelRSVP) before making it into [this package](https://github.com/alexholcombe/mixRSVP).
